Refinement for open automata

### 2021-05-12 2021-Refinement/report.tex
Sync

Values will be used for keeping a variable state, and then injected in terms for substitution.
This is correct when \(\values \subseteq \rterms\) and we suppose it is the case.
Otherwise it doesn't invalidates theorem because it can stand as a shorthand for substitution with any term which is interpreted as \(v\).
We suppose that the interpretation of terms is compatible w.r.t.\@ substitution, that is if two terms \(t\), \(t'\) are interpreted with the same value, then replacing \(t\) by \(t'\) in a well-formed expression makes an equivalent well-formed expression.
\begin{noti}[Notations for separating external logic and logic on \(\formulae\)]
\defitem The satisfiability relation will be noted using the classical relational notation \(\vdash f\).
\defitem The satisfiability of a formula \(f \in \formulae\) under some valuation \(\sigma: V \to \values\) is noted:
\[ \sigma \vdash f \defnotation \vdash \exists \fvars{f\psubst{\sigma}}, f\psubst{\sigma} \]
\defitem The satisfiability of a formula \(f \in \formulae\) with some variable set \(V\) as context is noted:
\[ V \vdash f \defnotation \vdash \forall V, \exists\mpar{\fvars{f} \setminus V}, f \]
\defitem The precedence of \(\vdash\) is the lowest on the right side and higher than \(\uplus\) on the left side:
\[ \forall a \, b, a \uplus b \vdash x \wedge y \implies \exists z, P\mpar{x,z} \text{ is the same as } \forall a \, b, \mpar{\mpar{a \uplus b} \vdash \mpar{\mpar{x \wedge y} \implies \exists z, P\mpar{x,z}}} \]
\end{noti}
With these common definitions and notations settled, the objects of interest can now be defined.
\begin{defi}[Open automaton]
A open automaton is a tuple \(\OA{S}{s_0}{V}{\sigma_0}{J}{T}\) with \(S\) the set of states, \(s_0 \in S\) the initial state, \(V\) the set of variable names unique to this automaton, \(\sigma_0: V' \to \values\) the initial valuation of variables where \(V' \subseteq V\), \(J\) the set of hole names and \(T\) the set of open transitions.

@@

The important properties we will consider here are:
\begin{defi} A relation \(\leq\) is
\defitem \textbf{reflexive} iff \(\forall a, a \leq a\);
\defitem \textbf{transitive} iff \(\forall a\, b\, c, a \leq b \wedge b \leq c \implies a \leq c\);
\defitem \textbf{a preorder} iff it is reflexive and transitive;
\defitem \textbf{correct w.r.t.\@ composition} iff \(\forall a\, b, a\mbrk{b} \leq a\);
\defitem \textbf{complete w.r.t.\@ composition} iff \(\forall a\, b, a \leq b \implies \exists c, a \overset{FH}= b\mbrk{c}\);
\defitem \textbf{context refining for composition} iff \(\forall a\, b\, c, a \leq b \implies a\mbrk{c} \leq b\mbrk{c}\);
\defitem \textbf{congruent for composition} iff \(\forall a\, b\, c, a \leq b \implies c\mbrk{a} \leq c\mbrk{b}\);
\defitem \textbf{compatible with composition} iff \(\forall a\, b\, c\, d, a \leq b \wedge c \leq d \implies c\mbrk{a} \leq d\mbrk{b}\);
\defitem \textbf{compatibile with FH-bisimulation} iff \(\forall a\, b\, c, d, a \overset{FH}= b \wedge c \overset{FH}= d \wedge a \leq c \implies b \leq d\).
\end{defi}
Reflexivity, transitivity and preorder are classical properties on relations.
Correctness w.r.t.\@ composition is the fact that every composition is considered a refinement.
Completeness w.r.t.\@ composition is the fact that a refinement correspond to the left automaton being equivalent to some composition of the right automaton.
Context refinement is the refinement being compatible with composition of the same automaton.
Congruence is the refinement being compatible with being composed in the same automaton.
Compatibility with composition is the conjunction of the two latter (assuming the relation is a preorder).
Finally compatibility with FH-bisimulation is the refinement not being able to distinguish two FH-bisimilar automata.

@@

Two states \(s_1 \in S_1, s_2 \in S_2\) with their respective valuations \(\sigma_1: V_1 \to \values, \sigma_2: V_2 \to \values\) are related iff \(\sigma_1 \uplus \sigma_2 \vdash R\mpar{s_1, s_2}\).
For a relation \(\wrel{}{}{}\) which uses a relation under predicate to prove that two element are related \(\forall x \, x', x \wrel{}{}{} x' \iff \exists R, P\mpar{R}\), the fact that there is a valid witness \(R\) is noted \(\wrel{x}{x'}{R}\).
\end{defi}
Now the properties about states of automata can be adapted to open automata.
\begin{defi}[Simulation on open automata]
A relation \(\leq\) is a simulation if for any two related automata \(\wrel{A_1}{A_2}{R}\) where \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\), \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and \(R: S_1 \times S_2 \to \rformulae[V_1 \uplus V_2]\), \(R\) satisfies both
\defitem Initial states are related under initial valuations: \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\);
\defitem From related states, all out-transitions from \(A_1\) can be simulated in \(A_2\) and their target states are \Ludo{related}{I am a bit surprised that $J_1$ and $J_2$ are unrelated and we only need to take only the intersection TBD}:
\begin{multline*}
	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \forall \sigma: V_1 \uplus V_2 \uplus \fvars{t_1} \to \values, \\
	\mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \\
	\sigma \uplus \nu \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
\end{multline*}
\end{defi}
The last formula means that for every pair of related states under valuation of the automaton variables and every possible transitions (\(\vdash g_1\)) from the first automaton, there is a possible transition (\(\vdash g_2\)) such that the produced action matches (\(\alpha_1 = \alpha_2\)), the holes actions from same hole names (\(J'_1 \cap J'_2\)) match (\(\beta_{1j} = \beta_{2j}\)) and the target states are related after variable update.
This is a natural extension of the notion of simulation on LTS, which is the same definition without variables and holes and guards.
It will serve as a watchdog for any relation that will be defined with ``simulation" in its name, except weak-simulation where the transition from the first automaton that produce \(\tau\) actions are excluded.

@@

``Deadlock reduction" conflicts with ``composition completeness" by disallowing some unwanted cases where an automaton in a hole cannot produce any action that any out-transitions expects.
In particular filling a hole with the deadlock automaton (only one state without out-transitions) is not considered a refinement for a \Ludo{deadlock reducing simulation refinement}{define or use the name of the definition}.
A way to solve this \Ludo{issue}{why is this an issue? can be solved by stating which properties are desirable for which reason above} is to characterise a composition that do not introduce deadlocks, which will be used instead of the composition introduced earlier.
\begin{defi}[Reachability]
For any open automata \(A \defobject \OA{S}{s_0}{V}{\sigma_0}{J}{T}\), a reachability predicate \(\reach{A}: S \to \rformulae[V]\) is a predicate on states such that
\defitem \(\sigma_0 \vdash \reach{A}\mpar{s_0}\).
\defitem \nmm{\bigsymb{\forall} t \defobject \OTg \in T, \forall \nu: \fvars{t} \to \values, \nu \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}}.
\end{defi}

@@

\begin{defi}[Deadlock reduction, working definition]
A simulation \(\leq\) is deadlock reducing if in all the \(R: S_1 \times S_2 \to \rformulae[V_1 \uplus V_2]\) such that \(\wrel{A_1}{A_2}{R}\), there is one that also satisfies
\begin{multline*}
	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V_1 \uplus V_2 \uplus \bigcup_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values, \\
	\sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
\end{multline*}
\Ludo{New Question}{what is the meaning of sigma here: it is not used on the right hand side of the implication; this seem to mean if there is  a sigma such that s1 and s2 are related then we have thr peoperty on disujunction on pred qithout caring about the valuation. Am I right? same question for the def below}
\Quentin{Reply}{Any variable not defined by the valuation is under an implicit \(\exists\) quantifier (satisfiability). What it means is that for every valuation where states are related and a transition is possible (disjunction on the left), there is a value for the free variables of the disjunction on the right that makes a transition possible (the existential quantifier has been wisely displaced in this explaination to make it easier to understand).}
\end{defi}
% TODO: Explain this formulations (it will also do the job of explaining the definition below)
\begin{lem}
The intuitive and working definition of deadlock reduction are equivalent.
\end{lem}

@@

\section{Refinement relations in restricted cases}\label{sec:prelref}
\Ludo{organisation}{Is this only preliminaries, if yes could it be placed earlier? if no perhaps rename into refinement for open automata something}
The main goal of this section is to help the reader understand the problems, constraints and different elements involved to solve them so that they are not all introduced at once in the real refinement relation.
The main objective of the refinement relations \Ludo{in this section}{du coup la on se pose la question est ce juste ici ou est ce le but global, c est quio le schema general? ceci dit ca sera peut etre resolu par l introduction ... mais dans tous les cas une petite couche sur ou on est et ou on va ca serait bien. il faut quelque part clairemetn definir ce qu on veut et sous quelle condition plus tot que ici} is to be able to state that a composition of two automata is a refinement of the base automaton (\(a\mbrk{b} \leq a\)) in restricted interesting cases. % TODO: probably remove, this is was written when the previous section was not yet written
\Ludo{lost}{I do not understand the last sentence}
Hopefully they can be used as simpler (and less expensive) versions of the real refinement relation in the case the manipulated automata respect the constraints.

@@

The specificities of open automata at on the relation between the (initial) states.
\Ludo{lost}{When reading the next sentences I am not sure where we are going, what is notation introduction of concepts or definitions, please clarify}
The relation \(R\) relates \(i_1\) to \(i_2\) under the condition that the current value of variables satisfies \(R\mpar{i_1, i_2}\).
If two states \(s_1 \in S_1, s_2 \in S_2\) are not(/never) related then \(\nvdash R\mpar{s_1, s_2}\).
The predicate \(R\mpar{i_1, i_2}\) is used to take into account the fact that a state is also constituted of the value of the variables.
This is already used in FH-bisimulation introduced in previous articles about open automata.
\Ludo{OK}{I guess I understand that you want to reach the next sentence as an explanation of the notations used in the definition, I mainly believe it is necessary to re-organise the ideas before}
So the meaning of \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\) is that the initial states with the initial valuation are effectively related. % TODO: Also a relic of the past, when things were explained on the go instead of in a dedicated section. Remove if already explained, move otherwise
\newpage % TODO: remove when less comments :)

@@

The notion of refinement here is stating that \(A_1\) is a refinement of \(A_2\) if \(A_1\) can be simulated \Ludo{in}{by?} \(A_2\).
The hole-identical part is referring to the fact that holes indices are the same and identical holes indices have to perform the same actions.
On top of that the last line ensures that no deadlock is introduced.
It can be interpreted ``assuming the predicate holds and there is any possible transition in \(A_2\) (= no deadlock), then there must be a possible transition in \(A_1\) (= no deadlock)''.
It does not have to ensure that this transition isn't garbage or that the target states are related because the first part of the simulation already does it.
Also if there was a deadlock then there is no transition because no transition can be simulated in a deadlock, that's why it is more a deadlock equivalence than a deadlock reduction.\Ludo{?}{the last sentence is not very clear}

@@

The first property is one part of the hole-identical simulation, the second property is the central part of the \Ludo{refinement simulation requirement}{add reference to def}.

@@

\Ludo{One may wonder why it was not used}{rephrase and state in what sense this second one could be considered as better} in the definition if it is equivalent.

>>>>

Values will be used for keeping a variable state, and then injected in terms for substitution.
This is correct when \(\values \subseteq \rterms\) and we suppose it is the case.
Otherwise it doesn't invalidates theorem because it can stand as a shorthand for substitution with any term which is interpreted as \(v\).
We suppose that the interpretation of terms is compatible w.r.t.\@ substitution, that is if two terms \(t\), \(t'\) are interpreted with the same value, then replacing \(t\) by \(t'\) in a well-formed expression makes an equivalent well-formed expression.
\begin{noti}[Notations for separating external logic and logic on \(\formulae\)]
\defitem The satisfiability relation will be noted using the classical relational notation \(\vdash f\).
\defitem The satisfiability of a formula \(f \in \formulae\) under some valuation \(\sigma: V \to \values\) is noted:
\[ \sigma \vdash f \defnotation \vdash \exists \fvars{f\psubst{\sigma}}, f\psubst{\sigma} \]
\defitem The satisfiability of a formula \(f \in \formulae\) with some variable set \(V\) as context is noted:
\[ V \vdash f \defnotation \vdash \forall V, \exists\mpar{\fvars{f} \setminus V}, f \]
\defitem The precedence of \(\vdash\) is the lowest on the right side and higher than \(\uplus\) on the left side:
\[ \forall a \, b, a \uplus b \vdash x \wedge y \implies \exists z, P\mpar{x,z} \text{ is the same as } \forall a \, b, \mpar{\mpar{a \uplus b} \vdash \mpar{\mpar{x \wedge y} \implies \exists z, P\mpar{x,z}}} \] % Mettre des niveaux de parenthèses
\end{noti}
With these common definitions and notations settled, the objects of interest can now be defined.
\begin{defi}[Open automaton]
A open automaton is a tuple \(\OA{S}{s_0}{V}{\sigma_0}{J}{T}\) with \(S\) the set of states, \(s_0 \in S\) the initial state, \(V\) the set of variable names unique to this automaton, \(\sigma_0: V' \to \values\) the initial valuation of variables where \(V' \subseteq V\), \(J\) the set of hole names and \(T\) the set of open transitions.

@@

The important properties we will consider here are:
\begin{defi} A relation \(\leq\) is
\defitem \textbf{reflexive} iff \(\forall a, a \leq a\);
\defitem \textbf{transitive} iff \(\forall a\, b\, c, a \leq b \wedge b \leq c \implies a \leq c\);
\defitem \textbf{a preorder} iff it is reflexive and transitive;
\defitem \textbf{correct w.r.t.\@ composition} iff \(\forall a\, b, a\mbrk{b} \leq a\);
\defitem \textbf{complete w.r.t.\@ composition} iff \(\forall a\, b, a \leq b \implies \exists c, a \overset{FH}= b\mbrk{c}\);
\defitem \textbf{context refining for composition} iff \(\forall a\, b\, c, a \leq b \implies a\mbrk{c} \leq b\mbrk{c}\);
\defitem \textbf{congruent for composition} iff \(\forall a\, b\, c, a \leq b \implies c\mbrk{a} \leq c\mbrk{b}\);
\defitem \textbf{compatible with composition} iff \(\forall a\, b\, c\, d, a \leq b \wedge c \leq d \implies c\mbrk{a} \leq d\mbrk{b}\);
\defitem \textbf{compatible with FH-bisimulation} iff \(\forall a\, b\, c, d, a \overset{FH}= b \wedge c \overset{FH}= d \wedge a \leq c \implies b \leq d\).
\end{defi}
Reflexivity, transitivity and preorder are classical properties on relations.
Correctness w.r.t.\@ composition is the fact that every composition is considered a refinement.
Completeness w.r.t.\@ composition is the fact that a refinement correspond to the left automaton being equivalent to some composition of the right automaton.
Context refinement is the refinement being compatible with composition of the same automaton.
Congruence is the refinement being compatible with being composed in the same automaton.
Compatibility with composition is the conjunction of the two latter (assuming the relation is a preorder).
Finally compatibility with FH-bisimulation is the refinement not being able to distinguish two FH-bisimilar automata.

@@

Two states \(s_1 \in S_1, s_2 \in S_2\) with their respective valuations \(\sigma_1: V_1 \to \values, \sigma_2: V_2 \to \values\) are related iff \(\sigma_1 \uplus \sigma_2 \vdash R\mpar{s_1, s_2}\).
For a relation \(\wrel{}{}{}\) which uses a relation under predicate to prove that two element are related \(\forall x \, x', x \wrel{}{}{} x' \iff \exists R, P\mpar{R}\), the fact that there is a valid witness \(R\) is noted \(\wrel{x}{x'}{R}\).
\end{defi}
Now the properties about states of automata can be adapted to open automata.
\begin{defi}[Simulation on open automata] % TODO: faire une définition standard
A relation \(\leq\) is a simulation if for any two related automata \(\wrel{A_1}{A_2}{R}\) where \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\), \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and \(R: S_1 \times S_2 \to \rformulae[V_1 \uplus V_2]\), \(R\) satisfies both
\defitem Initial states are related under initial valuations: \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\);
\defitem From related states, all out-transitions from \(A_1\) can be simulated in \(A_2\) and their target states are \Ludo{related}{I am a bit surprised that $J_1$ and $J_2$ are unrelated and we only need to take only the intersection TBD}:
\begin{multline*} % Mettre des sets de noms en commun qu'on veut effectivement mapper pour la transitivité
	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \forall \sigma: V_1 \uplus V_2 \uplus \fvars{t_1} \to \values, \\
	\mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \\
	\sigma \uplus \nu \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
\end{multline*}
\end{defi}
The last formula means that for every pair of related states under valuation of the automaton variables and every possible transitions (\(\vdash g_1\)) from the first automaton, there is a possible transition (\(\vdash g_2\)) such that the produced action matches (\(\alpha_1 = \alpha_2\)), the holes actions from same hole names (\(J'_1 \cap J'_2\)) match (\(\beta_{1j} = \beta_{2j}\)) and the target states are related after variable update.
This is a natural extension of the notion of simulation on LTS, which is the same definition without variables and holes and guards.
It will serve as a watchdog for any relation that will be defined with ``simulation" in its name, except weak-simulation where the transition from the first automaton that produce \(\tau\) actions are excluded.

@@

``Deadlock reduction" conflicts with ``composition completeness" by disallowing some unwanted cases where an automaton in a hole cannot produce any action that any out-transitions expects.
In particular filling a hole with the deadlock automaton (only one state without out-transitions) is not considered a refinement for a \Ludo{deadlock reducing simulation refinement}{define or use the name of the definition}. % Unfold a little bit and remove refinement
A way to solve this \Ludo{issue}{why is this an issue? can be solved by stating which properties are desirable for which reason above} is to characterise a composition that do not introduce deadlocks, which will be used instead of the composition introduced earlier. % Issue référence le conflit mais ce n'est pas clair, clarifie ça, replace issue with conflict
\begin{defi}[Reachability]
For any open automata \(A \defobject \OA{S}{s_0}{V}{\sigma_0}{J}{T}\), a reachability predicate \(\reach{A}: S \to \rformulae[V]\) is a predicate on states such that
\defitem \(\sigma_0 \vdash \reach{A}\mpar{s_0}\).
\defitem \nmm{\bigsymb{\forall} t \defobject \OTg \in T, \forall \nu: \fvars{t} \to \values, \nu \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}}.
\end{defi}

@@

\begin{defi}[Deadlock reduction, working definition]
A simulation \(\leq\) is deadlock reducing if in all the \(R: S_1 \times S_2 \to \rformulae[V_1 \uplus V_2]\) such that \(\wrel{A_1}{A_2}{R}\), there is one that also satisfies
\begin{multline*}
	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V_1 \uplus V_2 \uplus \bigcup_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values, \\
	\sigma \vdash \mpar{R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
\end{multline*}
\end{defi}
% TODO: Explain this formulations (it will also do the job of explaining the definition below)
\begin{lem}
The intuitive and working definition of deadlock reduction are equivalent.
\end{lem}

@@

\section{Refinement relations in restricted cases}\label{sec:prelref}
The main goal of this section is to help the reader understand the problems, constraints and different elements involved to solve them so that they are not all introduced at once in the real refinement relation.
The main objective of the refinement relations \Ludo{in this section}{du coup la on se pose la question est ce juste ici ou est ce le but global, c est quio le schema general? ceci dit ca sera peut etre resolu par l introduction ... mais dans tous les cas une petite couche sur ou on est et ou on va ca serait bien. il faut quelque part clairemetn definir ce qu on veut et sous quelle condition plus tot que ici} is to be able to state that a composition of two automata is a refinement of the base automaton (\(a\mbrk{b} \leq a\)) in restricted interesting cases. % TODO: probably remove, this is was written when the previous section was not yet written
\Ludo{lost}{I do not understand the last sentence}
Hopefully they can be used as simpler (and less expensive) versions of the real refinement relation in the case the manipulated automata respect some constraints.

@@

The specificities of open automata at on the relation between the (initial) states.
\Ludo{lost}{When reading the next sentences I am not sure where we are going, what is notation introduction of concepts or definitions, please clarify}
The relation \(R\) relates \(i_1\) to \(i_2\) under the condition that the current value of variables satisfies \(R\mpar{i_1, i_2}\).
If two states \(s_1 \in S_1, s_2 \in S_2\) are not(/never) related then \(\nvdash R\mpar{s_1, s_2}\).
The predicate \(R\mpar{s_{01}, s_{02}}\) is used to take into account the fact that a state is also constituted of the value of the variables.
This is already used in FH-bisimulation introduced in previous articles about open automata.
\Ludo{OK}{I guess I understand that you want to reach the next sentence as an explanation of the notations used in the definition, I mainly believe it is necessary to re-organise the ideas before}
So the meaning of \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\) is that the initial states with the initial valuation are effectively related. % TODO: Also a relic of the past, when things were explained on the go instead of in a dedicated section. Remove if already explained, move otherwise
\newpage % TODO: remove when less comments :)

@@

The notion of refinement here is stating that \(A_1\) is a refinement of \(A_2\) if \(A_1\) can be simulated \Ludo{in}{by?} \(A_2\).
The hole-identical part is referring to the fact that holes indices are the same and identical holes indices have to perform the same actions.
On top of that the last line ensures that no deadlock is introduced.
It can be interpreted ``assuming the predicate holds and there is any possible transition in \(A_2\) (= no deadlock), then there must be a possible transition in \(A_1\) (= no deadlock)''.
It does not have to ensure that this transition isn't garbage or that the target states are related because the first part of the simulation already does it.
Also if there was a deadlock then there is no transition because no transition can be simulated in a deadlock.
In that regard deadlock reduction caracterises in fact the absence of deadlock creation.\Ludo{?}{the last sentence is not very clear}

@@

The first property is one part of the hole-identical simulation, the second property is the central part of the \Ludo{refinement simulation requirement}{add reference to def (like "def x")}.

@@

\Ludo{One may wonder why it was not used}{rephrase and state in what sense this second one could be considered as better} in the definition if it is equivalent. % Informal!
